Model Adaptivity for Goal-Oriented Inference using Adjoints

### 2016-11-10 paper/numerical_experiments_v2_kw.tex
add comments from karen on version 2 (not on abstract or intro yet); create v3 files to start incorporating these comments

\section{Numerical Experiments}\label{sec:numexp}
%
We now use \cref{alg:refSeries} to solve goal-oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}. We first consider simple two-dimensional models in order to explore the behavior of the algorithm as well as the effect of varying the placement of observations and QoI regions. In \cref{sec:cdvcdr}, the high-fidelity model is a convection-diffusion-reaction nonlinear model, and the low-fidelity model is a linear convection-diffusion model. We apply \cref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region. In \cref{sec:constvfield}, both the high- and low-fidelity models are convection-diffusion-reaction nonlinear models, but they differ in how the parameter is represented. In \cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models.

@@

%------------------------------------------------------------------------------------------------------------------------%
\subsection{Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
%------------------------------------------------------------------------------------------------------------------------%
In this section, we consider a pair of models which differ in the physics included. In \cref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem. \Cref{sec:cdvcdrBaseRef} describes the results of applying \cref{alg:refSeries} to the baseline problem, and \cref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
%
%------------------------------------------------------------%
\subsubsection{Problem Setup} \label{sec:cdvcdrSetup}
%------------------------------------------------------------%
%
We consider a rectangular domain $\Omega(x_1,x_2)=[0,5]\times[0,1]$, where $x_1$ and $x_2$ are the spatial coordinates. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by,
%
\begin{subequations}
\label{eq:cdvcdrHF}
\begin{align}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:cdvcdrHF_int} \\
u = 0 \quad &\text{on } \partial \Omega \label{eq:cdvcdrHF_bdry}
\end{align} 
\end{subequations}
%
where the state $u$ is the species concentration and $f(q)$ is a forcing field described by the parameters. We have a divergence-free parabolic-profile velocity field $\vec{V}(x_1,x_2) = (2x_2(1-x_2),0)$; the diffusion and reaction coefficients are $k_d = 0.1$ and $k_r = -42.0$, respectively. The low-fidelity model,
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u = f(q)
\end{equation}
%
differs only in the removal of the reaction term. To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively. The resulting mixed-fidelity models can be described by, 
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k^{MF}_ru^2= f(q),
\end{equation}
%
where $k^{MF}_r$ is a piecewise-constant reaction coefficient,
%
\begin{equation}
k^{MF}_r=
\begin{cases}
k_r & \textrm{if }x\in\Omega_{HF} \\
0 & \textrm{if }x\in\Omega_{LF}.
\end{cases}
\end{equation}
%
Homogeneous Dirichlet boundary conditions are applied on the entire boundary of the domain. The QoI we wish to calculate is the integral of the state,
%
\begin{equation}
I(q,u)=\int_{(x_1,x_2)\in \Omega_I} u \:\textrm{d}A,
\end{equation}
%
over a region $\Omega_I=[0.625,0.875]\times[0.375,0.625]$.

The unknown parameters we wish to infer correspond to the forcing field, so that $f(q)=q$. For the low-fidelity model, the inverse problem is linear (the inferred parameters are linear in the observations). Synthetic observations consisting of the state at three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with the true forcing field
%
\begin{equation}
f_{true}(x_1,x_2)=
\begin{cases}
1.0 & \textrm{if }(x_1,x_2)\in[0.125,0.375]\times[0.125,0.375] \\
0.8 & \textrm{if }(x_1,x_2)\in[2.375,2.625]\times[0.375,0.625] \\
0 & \textrm{otherwise}.
\end{cases}
\end{equation}
%
The locations of the observations and the region $\Omega_I$ over which the QoI is calculated are shown in \cref{fig:baseSetup}. Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient. 
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
\caption{Locations of the observations and the QoI region.}
\label{fig:baseSetup}
\end{figure}
%

For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with Lagrange elements. We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations. 
%\red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...} 
The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable. The diffusion coefficient is such that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.
%
%------------------------------------------------------------%
\subsubsection{Adaptive Model Refinement Results} \label{sec:cdvcdrBaseRef} 
%------------------------------------------------------------%
%

@@

\Cref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. Each linear Lagrange basis function's contribution is plotted at its nonzero node.
%
\begin{figure}[htbp]
%\captionsetup[subfloat]{captionskip=-5pt}
\centering
\subfloat[LF $\equiv$ MF$_0$ ($0\%$ HF)]{
  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_LF_divvy.png}
  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_LF.png}
  \label{fig:baseRef0}
} \\
\subfloat[MF$_1$ ($5\%$ HF)]{
  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF01.png}
} \\
\subfloat[MF$_2$ ($10\%$ HF)]{
  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF02.png}
} \\
\caption{Local error contributions (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.}
\label{fig:baseRef}
\end{figure}
%
Note that the error contribution of each basis function whose support is entirely within the high-fidelity regions is zero.

We see that the largest local error contribution is concentrated in the QoI region, and the data point closest to the QoI. In the first decomposition of the error (\cref{fig:baseRef0}), the region where the elemental error is maximum is the leftmost data point. Since the constraining model is an elliptic PDE, with weak convection, information flow is localized, and is weakly convected from left to right. Therefore, for the calculation of the QoI, it is most important to refine the region near the leftmost data point, and the QoI region. After that, the error decomposition suggests refinement in regions upstream and around the middle data point, and then the rightmost data point.

\Cref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by \cref{alg:refSeries}; the true and estimated relative errors are calculated relative to the true and estimated high-fidelity QoI, respectively. In this case, we see that QoI error of $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain. We note that, in general, there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
\label{fig:baseErr}
\end{figure}
%

%------------------------------------------------------------%
\subsubsection{Interaction of Observations and QoI} \label{sec:qoivdata}
%------------------------------------------------------------%
%
The error estimate decomposition suggests the use of the high-fidelity model in areas of the domain that are important to the interaction between the observations and QoI; the interaction between these two can be complex, and the areas suggested for refinement may be nonintuitive. To see this, we compare the error estimate decomposition for three sizes of the QoI region $\Omega_I$ given the same set of data points, and for three nested sets of data points given the same QoI region. For the sake of illustration, we make two refinement iterations for each combination of observations and QoI region, regardless of the magnitude of the relative error estimate. However, it was noticed that the number of iterations needed to achieve a given tolerance increased as the QoI region increased.

The error decompositions for three increasingly large, nested QoI regions $\Omega_I$ given the same set of observations are shown in \cref{fig:qoiStudy}. The bottom row gives the baseline case presented in \cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, so the proportion of additional refined elements in each iteration is slightly larger. Although refinement is still most important around the data point closest to $x_1=0$, as the QoI region expands the other two data points become more important in that the error decomposition suggests refinement around them earlier. As the QoI region expands, it is also more clearly noticeable that refinement is not equally important in all parts of the QoI region.

\begin{figure}[htbp]
\centering
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_setup.png}
  \label{subfig:obsSetup}
}
\subfloat[MF$_0$ ($0\%$ HF)][LF $\equiv$ MF$_0$ \\($0\%$ HF)]{
  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err0.png}
  \label{subfig:obsLF}
}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err1.png}
}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2.png}
  \label{subfig:obsMFlast}
}
  \caption{With each row corresponding to the configuration of observations (teal points) and QoI region (purple box) shown in column \protect\subref{subfig:obsSetup}, compare the error estimate decompositions (columns \protect\subref{subfig:obsLF}-\protect\subref{subfig:obsMFlast}) given the same observations and different QoI regions.}
  \label{fig:qoiStudy}
\end{figure}

The error decomposition for three increasing, nested sets of observations and the same QoI region $\Omega_I$ is shown in \cref{fig:dataStudy}. Again, the bottom row gives the baseline case presented in \cref{sec:cdvcdrBaseRef}, although here the basis functions with the largest $5\%$ of the error are chosen, so the proportion of additional refined elements in each iteration is slightly larger. Refinement appears to be consistently most important around the data point closest to $x_1=0$ and the QoI region. However, as more data points are added, it becomes no longer necessarily true that refinement becomes less important around data points as their distance from the QoI region increases. The data points also interact with each other in that placing data points in regions of previously relatively uniform error contribution tends to result in a new error decomposition that is positive or negative around the data points, with valleys of zero magnitude in between.

\begin{figure}[htbp]
\centering
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_setup.png}
  \label{subfig:obsSetup2}
} 
\subfloat[MF$_0$ ($0\%$ HF)][LF $\equiv$ MF$_0$ \\($0\%$ HF)]{
  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err0.png}
  \label{subfig:obsLF2}
}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err1.png}
}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2.png}
  \label{subfig:obsMFlast2}
}
  \caption{With each row corresponding to the configuration of observations (teal points) and QoI region (purple box) shown in column \protect\subref{subfig:obsSetup2}, compare the error estimate decompositions (columns \protect\subref{subfig:obsLF2}-\protect\subref{subfig:obsMFlast2}) given different observations and the same QoI region.}
  \label{fig:dataStudy}
\end{figure}

%------------------------------------------------------------------------------------------------------------------------%
\subsection{Constant vs Field Parameters} \label{sec:constvfield}
%------------------------------------------------------------------------------------------------------------------------%

It is not necessary for the low- and high-fidelity models to differ in the physics included. A low-fidelity model may be more computationally tractable due to a reduced number of degrees of freedom rather than reduced nonlinearity. In this section, we consider two models which differ in the space to which the parameter belongs, with the low-fidelity model having fewer degrees of freedom.

@@

We consider the same high-fidelity model as in \cref{sec:cdvcdr}:
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U,
\end{equation}
with the same diffusion coefficient $k_d = 0.1$  and reaction coefficient $k_r = -42$. The low-fidelity model
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in\R
\end{equation}
differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field. Then the intermediate mixed-fidelity models have parameter fields which are non-constant in only portions of the domain. For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold. The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in \cref{sec:cdvcdr}. As the inverse problem is ill-posed, except for perhaps in the case where the low-fidelity model is used throughout the domain, regularization is added; the Tikhonov regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.

Although using such a pair of models has similarities to the problem of adaptive mesh refinement, we note that in this example only the parameter field changes in its level of refinement, not the state. Should the two models differ in the resolution of the state variables instead of the parameters, it is more efficient to use the approach discussed in \cite{BecVex05}.

@@

As with the previous examples in \cref{sec:cdvcdr}, the decomposition of the error estimate is used to select additional regions of the domain in which to use the high-fidelity model. The number of degrees of freedom in the inverse problem increases with the proportion of the domain in which the high-fidelity model is used and the unknown parameter allowed to be a field. With each iteration, an additional $10\%$ of the elements are marked for refinement. This is repeated until the estimated absolute relative error in the QoI, is less than $1\%$.

>>>>

\section{Numerical Experiments}\label{sec:numexp}
%
We now use \cref{alg:refSeries} to solve goal-oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}. We first consider two-dimensional models in order to explore the behavior of the algorithm as well as the effect of varying the placement of observations and QoI regions. In \cref{sec:cdvcdr}, the high-fidelity model is a convection-diffusion-reaction nonlinear model, and the low-fidelity model is a linear convection-diffusion model. We apply \cref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region. In \cref{sec:constvfield}, both the high- and low-fidelity models are convection-diffusion-reaction nonlinear models, but they differ in how the parameter is represented. In \cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models, again targeting a convection-diffusion-reaction problem.

@@

%------------------------------------------------------------------------------------------------------------------------%
\subsection{Variable Physics: Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
%------------------------------------------------------------------------------------------------------------------------%
In this section, we consider a pair of models which differ in the physics included. In \cref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem. \Cref{sec:cdvcdrBaseRef} describes the results of applying \cref{alg:refSeries} to the baseline problem, and \cref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
%
%------------------------------------------------------------%
\subsubsection{Problem Setup} \label{sec:cdvcdrSetup}
%------------------------------------------------------------%
%
We consider a rectangular domain $\Omega(x_1,x_2)=[0,5]\times[0,1]$, where $x_1$ and $x_2$ are the spatial coordinates. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by,
%
\begin{subequations}
\label{eq:cdvcdrHF}
\begin{align}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:cdvcdrHF_int} \\
u = 0 \quad &\text{on } \partial \Omega, \label{eq:cdvcdrHF_bdry}
\end{align}
\end{subequations}
%
where the state $u$ is the species concentration and $f(q)$ is a forcing field described by the parameters. We have a divergence-free parabolic-profile velocity field $\vec{V}(x_1,x_2) = (2x_2(1-x_2),0)$; the diffusion and reaction coefficients are $k_d = 0.1$ and $k_r = -42.0$, respectively. The low-fidelity model,
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u = f(q)
\end{equation}
%
differs only in the removal of the reaction term. To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively. The resulting mixed-fidelity models can be described by,
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k^{MF}_ru^2= f(q),
\end{equation}
%
where $k^{MF}_r$ is a piecewise-constant reaction coefficient,
%
\begin{equation}
k^{MF}_r=
\begin{cases}
k_r & \textrm{if }x\in\Omega_{HF} \\
0 & \textrm{if }x\in\Omega_{LF}.
\end{cases}
\end{equation}
%
Homogeneous Dirichlet boundary conditions are applied on the entire boundary of the domain. The QoI we wish to calculate is the integral of the state,
%
\begin{equation}
I(q,u)=\int_{(x_1,x_2)\in \Omega_I} u \:\textrm{d}A,
\end{equation}
%
over a region $\Omega_I=[0.625,0.875]\times[0.375,0.625]$.

The unknown parameters to be inferred correspond to the forcing field, so that in this case $f(q)=q$. The observations are sparse measurements of the state.
\cref{fig:baseSetup} shows the locations of the observations and the region $\Omega_I$ over which the QoI is calculated. For the low-fidelity model, the inverse problem is linear (i.e., the observations depend linearly on the parameters). Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient. % KW: term in what equation? give a reference or re-state the objective here.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
\caption{Locations of the observations and the QoI region.}
\label{fig:baseSetup}
\end{figure}
%

For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with Lagrange elements. We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations.
%\red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...}
The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable. The diffusion coefficient is such that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.

Synthetic observations consisting of the state at three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with the true forcing field
%
\begin{equation}
f_{true}(x_1,x_2)=
\begin{cases}
1.0 & \textrm{if }(x_1,x_2)\in[0.125,0.375]\times[0.125,0.375] \\
0.8 & \textrm{if }(x_1,x_2)\in[2.375,2.625]\times[0.375,0.625] \\
0 & \textrm{otherwise}.
\end{cases}
\end{equation}
%
%
%------------------------------------------------------------%
\subsubsection{Adaptive Model Refinement Results} \label{sec:cdvcdrBaseRef}
%------------------------------------------------------------%
%

@@

\Cref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. Each linear Lagrange basis function's contribution is plotted at its nonzero node.
%
\begin{figure}[htbp]
%\captionsetup[subfloat]{captionskip=-5pt}
\centering
\subfloat[LF $\equiv$ MF$_0$ ($0\%$ HF)]{
  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_LF_divvy.png}
  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_LF.png}
  \label{fig:baseRef0}
} \\
\subfloat[MF$_1$ ($5\%$ HF)]{
  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF01.png}
} \\
\subfloat[MF$_2$ ($10\%$ HF)]{
  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF02.png}
} \\
\caption{Left: Multi-fidelity refinement over the domain (low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion). Right: local error contributions. }
\label{fig:baseRef}
\end{figure}
%
Note that the error contribution of each basis function whose support is entirely within the high-fidelity regions is zero.

We see that the largest local error contribution is concentrated in the QoI region, and the data point closest to the QoI. 
% KW: I am not sure how to read the second phrase in this first sentence. Is it '...contribution is concentrated in two places: in the QoI region and near the observation location closest to the QoI.'  ??
In the first decomposition of the error (\cref{fig:baseRef0}), the region where the elemental error is maximum is the leftmost data point. % KW: again here, what is a 'data point' ? Do you mean 'observation location' ?
Since the constraining model is an elliptic PDE, with weak convection, information flow is localized, and is weakly convected from left to right. Therefore, for the calculation of the QoI, it is most important to refine the region near the leftmost data point, and the QoI region. % KW: same here. plus another confusing comma.
After that, the error decomposition suggests refinement in regions upstream and around the middle data point, and then the rightmost data point. % KW: and here

\Cref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by \cref{alg:refSeries}; the true and estimated relative errors are calculated relative to the true and estimated high-fidelity QoI, respectively. In this case, we see that QoI error of $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain. We note that while here the error is seen to decrease with increasing refinement, in general there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
\label{fig:baseErr}
\end{figure}
%

%------------------------------------------------------------%
\subsubsection{Interaction of Observations and QoI} \label{sec:qoivdata}
%------------------------------------------------------------%
%
The error estimate decomposition suggests the use of the high-fidelity model in areas of the domain that are important to the interaction between the observations and QoI; the interaction between these two can be complex, and the areas suggested for refinement may be nonintuitive. To see this, we compare the error estimate decomposition for three sizes of the QoI region $\Omega_I$ given the same set of data points, and for three nested sets of data points given the same QoI region. For the sake of illustration, we make two refinement iterations for each combination of observations and QoI region, regardless of the magnitude of the relative error estimate. However, in conducting the numerical experiments, it was observed that the number of iterations needed to achieve a given tolerance tended to increase as the QoI region increased.

\cref{fig:qoiStudy} shows the domain for three cases considered, with the same set of observations but increasingly large, nested QoI regions $\Omega_I$.
The error decompositions for each case are also shown in \cref{fig:qoiStudy}. The bottom row gives the baseline case presented in \cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, so the proportion of additional refined elements in each iteration is slightly larger.
% KW: I don't understand this last sentence. What's the difference with Section 4.1.2?
Although refinement is still most important around the data point closest to $x_1=0$, as the QoI region expands the other two data points become more important in that the error decomposition suggests refinement around them earlier. As the QoI region expands, it is also more clearly noticeable that refinement is not equally important in all parts of the QoI region.
% KW: fix references to 'data point' throughout.

\begin{figure}[htbp]
\centering
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_setup.png}
  \label{subfig:obsSetup}
}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err0.png}
  \label{subfig:obsLF}
}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err1.png}
}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2.png}
  \label{subfig:obsMFlast}
}
  \caption{Effects of increasing the QoI region. Column \protect\subref{subfig:obsSetup2}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}): the error estimate decompositions for different mixed-fidelity models.}
  \label{fig:qoiStudy}
\end{figure}

\cref{fig:dataStudy} shows another set of cases considered, now with the same QoI region $\Omega_I$ but with increasing, nested sets of observations.
The error decomposition for the three cases is shown in \cref{fig:dataStudy}. Again, the bottom row gives the baseline case presented in \cref{sec:cdvcdrBaseRef}, although here the basis functions with the largest $5\%$ of the error are chosen, so the proportion of additional refined elements in each iteration is slightly larger. Refinement appears to be consistently most important around the data point closest to $x_1=0$ and the QoI region. However, as more data points are added, it becomes no longer necessarily true that refinement becomes less important around data points as their distance from the QoI region increases. The data points also interact with each other in that placing data points in regions of previously relatively uniform error contribution tends to result in a new error decomposition that is positive or negative around the data points, with valleys of zero magnitude in between. % KW: I don't understand a lot of this discussion. You need to explain to me what you mean.

\begin{figure}[htbp]
\centering
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_setup.png}
  \label{subfig:obsSetup2}
}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err0.png}
  \label{subfig:obsLF2}
}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err1.png}
}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2.png}
  \label{subfig:obsMFlast2}
}
  \caption{Effects of increasing the number of observations. Column \protect\subref{subfig:obsSetup2}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}): the error estimate decompositions for different mixed-fidelity models.}
  \label{fig:dataStudy}
\end{figure}

%------------------------------------------------------------------------------------------------------------------------%
\subsection{Variable Parameterization: Constant vs.\ Field Parameters} \label{sec:constvfield}
%------------------------------------------------------------------------------------------------------------------------%

In this subsection, we consider two models which differ in the space to which the parameter belongs, with the low-fidelity model having fewer degrees of freedom.

@@

We consider the same high-fidelity model as in \cref{sec:cdvcdr}:
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U,
\end{equation}
with the same diffusion coefficient $k_d = 0.1$  and reaction coefficient $k_r = -42$. The low-fidelity model
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in\R
\end{equation}
differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field. The intermediate mixed-fidelity models thus have parameter fields that are constant over the subregions of the domain where the low-fidelity model is used. For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold. The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in \cref{sec:cdvcdr}. As the inverse problem is ill-posed, except for perhaps % KW: is it or not?
in the case where the low-fidelity model is used throughout the domain, regularization is added; % KW: added to what?
 the Tikhonov regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient. % KW: refer to the actual equation you are adding regularization to, or re-state the objective.

% KW: I'm commenting out this next statement, unless you strongly disagree.
%Although using such a pair of models has similarities to the problem of adaptive mesh refinement, we note that in this example only the parameter field changes in its level of refinement, not the state. Should the two models differ in the resolution of the state variables instead of the parameters, it is more efficient to use the approach discussed in \cite{BecVex05}.

@@

As with the previous examples in \cref{sec:cdvcdr}, the decomposition of the error estimate is used to select additional regions of the domain in which to use the high-fidelity model. The number of degrees of freedom in the inverse problem increases with the proportion of the domain in which the high-fidelity model is used. With each iteration, an additional $10\%$ of the elements are marked for refinement. This is repeated until the estimated absolute relative error in the QoI is less than $1\%$.
